The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Traditional Front-running Prevention Methods

\subsection{Literature on Traditional Front-running}
As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
%@shayan: ^ TODO!

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible. 
%@shayan: ^ TODO!

%______________________________________________________________%
\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases). In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.

>>>>

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\emph{Traditional Front-running Prevention Methods}. There are debates in traditional markets regarding the fact that Front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible. 
%______________________________________________________________%
\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases). In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.
